---
title: "Project1_Manip_Data"
author: "Marie Levet"
date: "26/09/2019"
output: 
  html_document:
   keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import the dataset into R studio 

Downloaded the csv file on Montreal city website 
Saved and placed within the "01_Levet" folder on the desktop

```{r import data into R} 
library(readxl) #fast excel reader
# import the data in R with file.choose 
Punaise_data <-read.csv("/Users/marielevet/Desktop/01_Levet/Punaise_Data.csv") # cheated with the path because I could not find another way to import the csv file. 
```

```{r import the library}
library (tidyr) # restructuring the data
library (dplyr) # doing calculation with the data 
library (ggplot2) # plot/visualise the data
library (magrittr) # to use the pipping function 
```

Exploring and restructuring the data 

```{r exploring the data}
#exploring the data
attach(Punaise_data) # to ease the manipulation with the data
View(Punaise_data) # to visualise the dataset
head (Punaise_data) # to see the first few rows of the data
summary(Punaise_data) # to get an idea of the stats on the dataset 

#restructuring the data
 Punaise_data2 <- Punaise_data[complete.cases(Punaise_data), ] # removing NA's from the dataset
 View(Punaise_data2) # double check that the NA's are gone
 attach (Punaise_data2)
 Punaise_data2 <- select (Punaise_data2, - COORD_X, - COORD_Y, - LONGITUDE, - LATITUDE) # create a subtract of dataset with columns of interest 
```

Plotting the data 
  
```{r Plotting the data}
# ploting the number of declarations per arrondissement to see the differences between area of the city 

ggplot(Punaise_data, aes (x = NOM_ARROND, y = NO_DECLARATION)) + 
  geom_point() +
  theme_classic() + # to remove the background 
  xlab ("Arrondissement") + ylab ("Nombre de déclaration") + # label x and y axes
  theme( axis.title.x = element_text(colour = "purple", 
size =rel(1.5)), axis.text.x = element_text(angle = 45, size = 10, vjust = 0.5)) + # adjust the label of the x axis to make it more visual (defined the angle, size of the title and the distance below the axis line) 
theme (axis.title.y = element_text(colour = "purple", size = rel(1.5)))
  
# plotting the number of extermination per arrondissements
ggplot(Punaise_data2, aes (x = NBR_EXTERMIN, y = NOM_ARROND)) +
  geom_boxplot() + 
  theme_classic() +
  xlab ("Nombre d'extermination") + ylab ("Arrondissement")
  